---
title: "Norming"
author: "Jeanne"
date: "August 26, 2024"
output: html_document
---
##NORMING THE STORIES FOR STUDY 1 (INTERVENTION STUDY)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(plyr)
library(lme4)
library(lmerTest)
```

```{r, echo = FALSE}

##loading the spreadsheet
normingData<-read.csv("intervention_normingData.csv", header=T,sep=",")

##renaming the columns
names(normingData)<-c("Subject", "Story","trial","totalWords","missed","percent","Coder")

##Make subject, list, story, trial, recording, and coder FACTORS
normingData$Subject<- factor(normingData$Subject)
normingData$Story<-factor(normingData$Story)
normingData$Coder<-factor(normingData$Coder)

##taking out IN06, and IN13 (non native speaker) and IN19 (did not do the task)   
normingData<-normingData[!normingData$Subject %in% c("IN06", "IN13", "IN19"),]
normingData$Subject<-factor(normingData$Subject)

##taking out rows that have empty cells (e.g. when a story was not play, missing data)
normingData.noNa<-na.omit(normingData)

(unique(normingData$Subject))

```

##Number of times each story appears in each position (from trial 1 to trial 8)   
This is the count without the missing data 
All stories appeared at least 2 times in each position (actually 3 for 7 stories out of 8) and at most 5 times. 

```{r, echo=FALSE}
ddply(normingData.noNa, .(Story,trial), summarise, number = length(unique(Subject)))


table(normingData.noNa$Story, normingData.noNa$trial)
```


##Mean percent word missed per subject

```{r, echo=FALSE}
##measures the mean percent of words missed for each subject + also the standard deviation
mean_subject<-aggregate(percent~Subject, normingData.noNa, FUN="mean")
sd_subjects <- aggregate(percent~Subject, normingData.noNa, FUN="sd")


##Calculate min and max percent missed, store in data frame
mins<-tapply(normingData.noNa$percent, normingData.noNa$Subject, min)
maxs<-tapply(normingData.noNa$percent, normingData.noNa$Subject, max)

##Add mins and maxs to mean_subject
mean_subject$min<-mins
mean_subject$max<-maxs

```

##Plot of all subjects' mean scores  
The red line is the overall means. Each bar represents a subject 
```{r, echo=FALSE}
ggplot(mean_subject, aes(Subject, percent))+
  geom_bar(stat = "identity", position="dodge")+
  geom_hline(yintercept = mean(mean_subject$percent), color="red")+
  ylim(0,30)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r, echo=FALSE}
## overall average 
mean(mean_subject$percent)

## overall SD
sd(mean_subject$percent)

## overall MIN AND MAX
min(mean_subject$percent)
max(mean_subject$percent)
```

The overall mean percent missed words was 4.65%, SD = 5.85 (so pretty good performance overall)  
IN25 clearly performed much worse than the other subjects. 

##Mean percent word missed per story  
Were some stories harder to shadow?  

```{r, echo=FALSE}
##calculating means, mins and max
mean_stories<-aggregate(percent~Story, normingData.noNa, FUN="mean")
mins<-tapply(normingData.noNa$percent, normingData.noNa$Story, min)
maxs<-tapply(normingData.noNa$percent, normingData.noNa$Story, max)

##put them all in one data frame
mean_stories$min<-mins
mean_stories$max<-maxs

##Standard error to the mean
sd_stories <- aggregate(percent~Story, normingData.noNa, FUN="sd")
sd_stories$sem<- sd_stories$percent/sqrt(29) ##29 is the number of subjects in the sample. 
mean_stories$sd<-sd_stories$percent
mean_stories$sem<-sd_stories$sem
```

##Plot of mean percent missed per story  
  
The blue line represents the overall mean, i.e., 4.7%
```{r, echo=FALSE}
#png("norming1_plot.png", units="in", width=8, height=7, res=300)

ggplot(mean_stories, aes(reorder(Story,-percent), percent))+
  geom_bar(stat = "identity", position="dodge", fill="#F8766D")+
  geom_hline(yintercept = mean(mean_stories$percent), color="#00BFC4", size = 1)+
   geom_errorbar(aes(ymin=percent-sem, ymax=percent+sem, shape=Story), width=.2,size=1, position=position_dodge(.9))+
  theme_minimal(base_size=16)+
  ylab("% words missed")+
  xlab("")+
  ylim(0,10)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#dev.off()
```

##Mean percent missed words per trial
```{r, echo=FALSE}
##calculating means, mins and max
mean_trial<-aggregate(percent~trial, normingData.noNa, FUN="mean")
mins<-tapply(normingData.noNa$percent, normingData.noNa$trial, min)
maxs<-tapply(normingData.noNa$percent, normingData.noNa$trial, max)

##Putting everything in one data frame
mean_trial$min<-mins
mean_trial$max<-maxs

##Standard error to the mean
sd_trial <- aggregate(percent~trial,normingData.noNa, FUN="sd")
sd_trial$sem<- sd_trial$percent/sqrt(25) #there are 25 subjects
mean_trial$sd<-sd_trial$percent
mean_trial$sem<-sd_trial$sem


mean_trial

#mean_trial$trial<-factor(mean_trial$trial)

```
##Plot by trial 
```{r, echo=FALSE}
ggplot(mean_trial, aes(trial, percent))+
  geom_bar(stat = "identity", position="dodge")+
  geom_hline(yintercept = mean(mean_trial$percent), color="red")+
  ylim(0,20)
```


##GLMER ANALYSIS
```{r}
##effect of story on percent word missed
##percent treated as continuous var non bounded

##trial and Story as a factor
#normingData.noNa$trial<-factor(normingData.noNa$trial)
#normingData.noNa$Story<-factor(normingData.noNa$Story)


mod1 <- (glmer(missed / totalWords ~ trial+Story +  (1+trial|Subject)+(1+trial|Story), weights = totalWords,
   family = binomial, data = normingData))

mod2 <- (glmer(missed / totalWords ~ trial +  (1+trial|Subject)+(1+trial|Story), weights = totalWords,
   family = binomial, data = normingData))

anova(mod1,mod2)

```

There is a significant effect of Story

```{r}
summary(mod1)
```

In particular, Ashley and Psychics is harder than Cat Videos, Father & Sons, Rabbit's Thesis and Tim's brilliant career.  


```{r}
##effect of trial? 


mod3 <- (glmer(missed / totalWords ~ Story +  (1+trial|Subject)+(1+trial|Story), weights = totalWords,
   family = binomial, data = normingData))

anova(mod1,mod3)
```


```{r}
summary(mod1)
```
There is also an effect of trial, reflecting a task learning effect 

## ANALYSIS WITHOUT THE FIRST TRIAL

```{r}
#without Ashley
normingData_no_first_trial <- normingData.noNa[!normingData.noNa$trial == 1,]
#normingData_no_first_trial$trial <- as.factor(normingData_no_first_trial$trial)

mod1_no_first_trial <- (glmer(missed / totalWords ~ trial+ Story +  (1+trial|Subject)+(1+trial|Story), weights = totalWords,
   family = binomial, data = normingData_no_first_trial))

mod2_no_first_trial <- (glmer(missed / totalWords ~ trial +  (1+trial|Subject)+(1+trial|Story), weights = totalWords,
   family = binomial, data = normingData_no_first_trial))

anova(mod1_no_first_trial,mod2_no_first_trial)

summary(mod1_no_first_trial)
```

The effect of trial disappears when taking out the first one. 

